---
title: "GAManalysis_study2_0-1000_final"
author: "Amélie la Roi"
date: "19 juli 2018"
output: html_document
---

Last update: November 2, 2020


This document contains the analysis of the data of study 2. This study consists of an eye-tracking experiment with a visual world paradigm. The screen was divided into four quadrants. In each trial, two of the trials contained a picture, while the other two quadrants remained empty. The dependent variable in the study is the proportion of looks to the target picture displaying the figurative meaning of an idiom. The figurative picture was shown together with a picture displaying the literal meaning of the idiom (competitor condition) or with a picture only including the last noun of the idiom, used in a situation that is unrelated to both the figurative and literal meaning of the idiom.


### Install and load packages
```{r install packages, eval=FALSE, warning='hide'}
library(devtools)
library(itsadug)
library(mgcv)
library(sp)

```

### Load data
```{r load data}

print(load(paste("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Data_no delay/YoungOld/Preprocessed/preprocessed_final.rdat")))

head(preprocessed_final)
dim(preprocessed_final) # more than 10000 datapoints, so use bam()
```

### Prepare data for model fitting
```{r prepare data}
# Check data
str(preprocessed_final)
summary(preprocessed_final)

# Make sure Participant, Condition, and IdiomType are factors
preprocessed_final$Participant <- as.factor(as.character(preprocessed_final$Participant))
preprocessed_final$Condition <- as.factor(preprocessed_final$Condition)
preprocessed_final$IdiomType <- as.factor(preprocessed_final$IdiomType)
preprocessed_final$Item <- as.factor(as.character(preprocessed_final$Item))

# Check contrasts
contrasts(preprocessed_final$Group)
preprocessed_final$Group <- relevel(preprocessed_final$Group, ref="younger adults")
contrasts(preprocessed_final$Group) # younger adults are reference level

contrasts(preprocessed_final$Condition)
preprocessed_final$Condition <- relevel(preprocessed_final$Condition, ref="distractor")
contrasts(preprocessed_final$Condition) # distractor is reference level

contrasts(preprocessed_final$IdiomType)
preprocessed_final$IdiomType <- relevel(preprocessed_final$IdiomType, ref="two-noun")
contrasts(preprocessed_final$IdiomType) # short idioms are reference level


# Check data again
str(preprocessed_final)

# Only select data starting between 0 - 1000 ms after sentence onset
sort(unique(preprocessed_final$Timebin))
expBegin <- droplevels(preprocessed_final[preprocessed_final$Timebin < 1000,])
sort(unique(expBegin$Timebin))

# Create Event variable
## Create interaction variable between Condition and IdiomType
expBegin$Event <- interaction(expBegin$Participant, expBegin$Item, drop=TRUE)

# # Log-transform proportions
# exp$LogTargetProp <- log(exp$TargetProp)

# Create start event column
expBegin <- start_event(expBegin, column="Timebin", event="Event")

# Create counts
expBegin$Counts <- cbind(Target=expBegin$TargetgazeSum, Other=expBegin$DistgazeSum)

# Create interaction variables
expBegin$GroupCond <- interaction(expBegin$Group, expBegin$Condition, drop=TRUE) # interaction between Group and Condition
expBegin$GroupType <- interaction(expBegin$Group, expBegin$IdiomType) # creates four reference levels for the four possible combinations of Group and IdiomType
expBegin$GroupCondType <- interaction(expBegin$Group, expBegin$Condition, expBegin$IdiomType, drop=TRUE) # interaction between Group, Condition, and IdiomType

# Center scores on Stroop, Dual task, and SART
expBegin$SartError_scale <- scale(expBegin$SartError, center=T, scale=T)
expBegin$Stroop_scale <- scale(expBegin$Stroop, center=T, scale=T)
expBegin$DualScore_scale <- scale(expBegin$DualScore, center=T, scale=T)

# Create binary predictors
## For Group factor
expBegin$IsOld <- ifelse(expBegin$Group=="elderly adults", 1, 0)
expBegin$IsYoung <- ifelse(expBegin$Group=="younger adults", 1, 0)

## For Condition factor
expBegin$IsComp <- ifelse(expBegin$Condition=="competitor", 1, 0)
expBegin$IsDist <- ifelse(expBegin$Condition=="distractor", 1, 0)

## For IdiomType facor
expBegin$IsTwo <- ifelse(expBegin$IdiomType=="two-noun", 1, 0)
expBegin$IsThree <- ifelse(expBegin$IdiomType=="three-noun", 1, 0)

# Create interaction variable between Group and Condition
expBegin$IsYoungComp <- (expBegin$Group=="younger adults" & expBegin$Condition=="competitor")*1
expBegin$IsOldComp <- (expBegin$Group=="elderly adults" & expBegin$Condition=="competitor")*1


expBegin$IsOldThree <- (expBegin$Group=="elderly adults" & expBegin$IdiomType=="three-noun")*1

# Binary predictors for full model including Idiom type
expBegin$IsCompTwo <- (expBegin$Condition=="competitor" & expBegin$IdiomType=="two-noun")*1 # difference distractor vs. competitor for two-noun idioms in younger adults

expBegin$IsCompThree <- (expBegin$Condition=="competitor" & expBegin$IdiomType=="three-noun")*1 # difference distractor vs. competitor for three-noun idioms in younger adults

expBegin$IsYoungCompTwo <- (expBegin$Group=="younger adults" &expBegin$Condition=="competitor" & expBegin$IdiomType=="two-noun")*1 # difference distractor vs. competitor for two-noun idioms in elderly adults

expBegin$IsYoungCompThree <- (expBegin$Group=="younger adults" &expBegin$Condition=="competitor" & expBegin$IdiomType=="three-noun")*1 # difference distractor vs. competitor for three-noun idioms in elderly adults

expBegin$IsOldCompTwo <- (expBegin$Group=="elderly adults" &expBegin$Condition=="competitor" & expBegin$IdiomType=="two-noun")*1 # difference distractor vs. competitor for two-noun idioms in elderly adults

expBegin$IsOldCompThree <- (expBegin$Group=="elderly adults" &expBegin$Condition=="competitor" & expBegin$IdiomType=="three-noun")*1 # difference distractor vs. competitor for three-noun idioms in elderly adults

# Save data for use in Peregrine
save(expBegin, file = "G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Data_no delay/YoungOld/Preprocessed/expBegin.rdat" )

print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Data_no delay/YoungOld/Preprocessed/expBegin.rdat"))

```


## Model fitting on counts
### Factor model
```{r}
# Basic model without rho value
mB0 <- bam(Counts ~ GroupCond 
          + s(Timebin, by=GroupCond) 
          + s(Timebin, Participant, bs="fs", m=1)
          + s(Timebin, Item, bs="fs", m=1)
          + s(Event, bs="re"),
          data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB0.rda"))

# Model summary
(mB0_sum <- summary(mB0, re.test=FALSE)) # 69% explained deviance

# Check fit of the model
gam.check(mB0) # k's may have to be increased
acf_resid(mB0) # there's autocorrelation, but binomial models can't include rho value


# Plot smooths per condition
plot_smooth(mB0, view="Timebin", plot_all="GroupCond", rug=F, shade=T)

plot_smooth(mB0, view="Timebin", cond=list(GroupCond=c("younger adults.distractor", "younger adults.competitor")))

plot_diff(mB0, view="Timebin", comp=list(GroupCond=c("younger adults.distractor", "younger adults.competitor")), shade=T)

plot_diff(mB0, view="Timebin", comp=list(GroupCond=c("elderly adults.distractor", "elderly adults.competitor")), shade=T)

```


## Binary model
### Averaged over two-word and three-word idioms
```{r}
# Binary model without rho value
## Fit difference between competitor and distractor condition separately for younger adults and elderly adults
mB0bin <- bam(Counts ~ Group 
                + s(Timebin, by=Group) 
                + s(Timebin, by=IsYoungComp) # models the difference distractor vs. competitor condition for younger adults
                + s(Timebin, by=IsOldComp) # models the difference distractor vs. competitor condition for elderly adults
                + s(Timebin, Participant, bs="fs", m=1)
                + s(Timebin, Item, bs="fs", m=1)
                + s(Event, bs="re"),
                data=expBegin, discrete=TRUE, family="binomial")

# Explanation model terms:
## Younger adults - distractor: s(Timebin): GroupYounger adults
## Younger adults - competitor: s(Timebin): GroupYounger adults + s(Timebin, by=IsYoungComp)
## Elderly adults - distractor: s(Timebin): GroupElderly adults
## Elderly adults - competitor: s(Timebin): GroupElderly adults + s(Timebin, by=IsOldComp)

### s(Timebin, by=IsYoungComp) models the difference distractor vs. competitor for younger adults
### s(Timebin, by=IsOldComp) models the difference distractor vs. competitor for elderly adults

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB0bin.rda"))

# Model summary
(mB0bin_sum <- summary(mB0bin, re.test=FALSE)) # 69% explained variance
                                             # Significant difference between conditions for both younger and elderly adults
# Check autocorrelation
acf_resid(mB0bin) # There's autocorrelation, but binary models can't account for autocorrelation

```

## Plot binary model
```{r}
par(mfrow=c(1,2))
# Plot smooth per condition for younger adults
## Distractor condition
plot_smooth(mB0bin, view="Timebin", cond=list(IsYoungComp=0, Group="younger adults"), rm.ranef=TRUE, n.grid=100, main="Younger adults\nDistractor vs. Competitor", col='blue', ylim=c(-2,6))
## Competitor condition
plot_smooth(mB0bin, view="Timebin", cond=list(IsYoungComp=1, Group="younger adults"), rm.ranef=TRUE, n.grid=100, col='red', add=T)

# Plot smooth per condition for elderly adults
## Distractor condition
plot_smooth(mB0bin, view="Timebin", cond=list(IsOldComp=0, Group="elderly adults"), rm.ranef=TRUE, n.grid=100, main="Elderly adults\nDistractor vs. Competitor", col='blue', ylim=c(-2,6))
## Competitor condition
plot_smooth(mB0bin, view="Timebin", cond=list(IsOldComp=1, Group="elderly adults"), rm.ranef=TRUE, n.grid=100, col='red', add=T)

# Add legend
gfc <- getFigCoords() # add legend
legend(gfc[2], gfc[4], legend = c("distractor","competitor"), text.col = c("blue","red"), text.font = 2, xjust = 1, yjust = 1 , bty = "n", xpd = TRUE)

# Plot difference between distractor and competitor condition for younger and elderly adults
## Younger adults
plot_diff(mB0bin, view="Timebin", comp=list(IsYoungComp=c(1,0)), cond=list(Group="younger adults"), rm.ranef=T, main="Difference distractor vs. competitor\nYounger adults", ylim=c(-2,2)) # difference between conditions ends at 1260 ms
## Elderly adults
plot_diff(mB0bin, view="Timebin", comp=list(IsOldComp=c(1,0)), cond=list(Group="elderly adults"), rm.ranef=T, main="Difference distractor vs. competitor\nElderly adults", ylim=c(-2,2)) # difference between conditions ends at 1700 ms

# Y-axis
## count = 0: 50% looking at target picture, 50% looking at distractor picture
## count = 25: 100% looking at target picture
## count = -25: 100% looking at distractor picture
```


### Fit binary model that directly models the in contrast distractor vs. competitor between younger and elderly adults (interaction effect)
```{r}
# Model without rho
mB1bin <- bam(Counts ~ Group + 
             + s(Timebin, by=Group) # models the smooth for the reference level younger adults - distractor
             + s(Timebin, by=IsComp) # models the difference distractor vs. competitor condition for younger adults
             + s(Timebin, by=IsOldComp) # models the difference distractor vs. competitor condition for elderly adults
             + s(Timebin, Participant, bs="fs", m=1)
             + s(Timebin, Item, bs="fs", m=1)
             + s(Event, bs="re"),
             data=expBegin, discrete=TRUE, family="binomial")


## Younger adults - distractor condition: s(Timebin):GroupYounger adults
## Younger adults - competitor condition: s(Timebin):GroupYounger adults + s(Timebin, by=IsComp)
## Elderly adults - distractor condition: s(Timebin):GroupElderly adults
## Elderly adults - competitor condition: s(Timebin):GroupElderly adults + s(Timebin, by=IsComp) + s(Timebin, by=IsOldComp) 


# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB1bin.rda"))

# Model summary
(mB1bin_sum <- summary(mB1bin, re.test=FALSE)) # 69 % explained deviance
                                             # Significant interaction

# Plot interaction smooth
plot(mB1bin, select=4, shade=T, ylim=c(-3,3), h=0)

# Check model fit
gam.check(mB1bin) # k's should be increased
                 # But first we should add a predictor for Idiom type

```


## Fit binary model that includes idiom type
```{r}
# Fit model
mB2bin <- bam(Counts ~ GroupType
             + s(Timebin, by=GroupType)
             + s(Timebin, by=IsYoungCompTwo)
             + s(Timebin, by=IsYoungCompThree)
             + s(Timebin, by=IsOldCompTwo)
             + s(Timebin, by=IsOldCompThree)
             + s(Timebin, Participant, bs="fs", m=1)
             + s(Timebin, Item, bs="fs", m=1)
             + s(Event, bs="re"),
             data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB2bin.rda"))

# Model summary
(mB2bin_sum <- summary(mB2bin, re.test=FALSE)) #  69.2 % explained deviance

# Check model fit 
gam.check(mB2bin) # increase k 

# Fit model with k=20
mB2bin20 <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsYoungCompTwo, k=20)
                  + s(Timebin, by=IsYoungCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB2bin20.rda"))

# Model summary
(mB2bin20_sum <- summary(mB2bin20, re.test=TRUE)) #  69.2 % explained deviance--> THIS IS REPORTED IN PAPER (Table 2)

# Save model summary
save(mB2bin20_sum, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB2bin20_sum.rda", compress='xz')

# Print model statistics
mB2bin20_stats <- report_stats(mB2bin20)
m2bin20_ML_stats <- report_stats(m2bin20_ML)

# Save model statistics
save(m2bin20_stats, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/m2bin20_stats.rda", compress='xz')

# Check model fit after increasing k 
gam.check(m2bin20) # not much better, but k cannot be increased further due to limited number of unique value
gam.check(m2bin20_ML) 
```


## Plot model with k=20
```{r}
# Y-axis
## count = 0: 50% looking at target picture, 50% looking at distractor picture
## count = 25: 100% looking at target picture
## count= -25: 100% looking at distractor picture


par(mfrow=c(2,2))

# Younger adults - Two-word idioms
##Distractor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=0, GroupType="younger adults.two-noun"), rm.ranef=TRUE, n.grid=100, main="Younger adults (k=20)\nDistractor vs. Competitor\nTwo-word idioms", col='blue', ylim=c(-3,6), v=266)
## Competitor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=1, IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=0, GroupType="younger adults.two-noun"), rm.ranef=TRUE, n.grid=100, col='red', add=T)

# Younger adults - Three-word idioms
##Distractor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=0, GroupType="younger adults.three-noun"), rm.ranef=TRUE, n.grid=100, main="Younger adults (k=20)\nDistractor vs. Competitor\nThree-word idioms", col='blue', ylim=c(-3,6), v=256)
## Competitor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=1, IsOldCompTwo=0, IsOldCompThree=0, GroupType="younger adults.three-noun"), rm.ranef=TRUE, n.grid=100, col='red', add=T)

# Elderly adults - Two-word idioms
##Distractor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=0, GroupType="elderly adults.two-noun"), rm.ranef=TRUE, n.grid=100, main="Elderly adults (k=20)\nDistractor vs. Competitor\nTwo-word idioms", col='blue', ylim=c(-3,6), v=266)
## Competitor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=1, IsOldCompThree=0, GroupType="elderly adults.two-noun"), rm.ranef=TRUE, n.grid=100, col='red', add=T)

# Elderly adults - Three-word idioms
##Distractor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=0, GroupType="elderly adults.three-noun"), rm.ranef=TRUE, n.grid=100, main="Elderly adults (k=20)\nDistractor vs. Competitor\nThree-word idioms", col='blue', ylim=c(-3,6), v=256)
## Competitor condition
plot_smooth(mB2bin20, view="Timebin", cond=list(IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=1, GroupType="elderly adults.three-noun"), rm.ranef=TRUE, n.grid=100, col='red', add=T)


# Add legend
gfc <- getFigCoords() # add legend
legend(gfc[2], gfc[4], legend = c("distractor","competitor"), text.col = c("blue","red"), text.font = 2, 
       xjust = 1, yjust = 1 , bty = "n", xpd = TRUE)


# Plot difference between distractor and competitor condition per Group and Idiom Type
par(mfrow=c(2,2))
## Younger adults - Two-word idioms
plot_diff(mB2bin20, view="Timebin", comp=list(IsYoungCompTwo=c(1,0)), cond=list(GroupType="younger adults.two-noun", IsYoungCompThree=0, IsOldCompTwo=0, IsOldCompThree=0), rm.ranef=T, main="Younger adults (k=20)\nDifference distractor vs. Competitor\nTwo-word idioms", ylim=c(-5,5), v=266)
## Younger adults - Three-word idioms
plot_diff(mB2bin20, view="Timebin", comp=list(IsYoungCompThree=c(1,0)), cond=list(GroupType="younger adults.three-noun", IsYoungCompTwo=0, IsOldCompTwo=0, IsOldCompThree=0), rm.ranef=T, main="Younger adults (k=20)\nDifference distractor vs. Competitor\nThree-word idioms", ylim=c(-5,5), v=256)

## Elderly adults - Two-word idioms
plot_diff(mB2bin20, view="Timebin", comp=list(IsOldCompTwo=c(1,0)), cond=list(GroupType="elderly adults.two-noun", IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompThree=0), rm.ranef=T, main="Elderly adults (k=20)\nDifference distractor vs. Competitor\nTwo-word idioms", ylim=c(-5,5), v=266)
## Elderly adults - Three-word idioms
plot_diff(mB2bin20, view="Timebin", comp=list(IsOldCompThree=c(1,0)), cond=list(GroupType="elderly adults.three-noun", IsYoungCompTwo=0, IsYoungCompThree=0, IsOldCompTwo=0), rm.ranef=T, main="Elderly adults (k=20)\nDifference distractor vs. Competitor\nThree-word idioms", ylim=c(-5,5), v=256)


```


### Fit binary model that includes idiom type and directly tests interaction Group x Condition
```{r}
# Fit model 
mB3bin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType)
                  + s(Timebin, by=IsCompTwo)
                  + s(Timebin, by=IsCompThree)
                  + s(Timebin, by=IsOldCompTwo)
                  + s(Timebin, by=IsOldCompThree)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/m3bin.rda"))

save(mB3bin, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB3bin.rda", compress='xz')

# Model summary
(m3bin_sum <- summary(m3bin, re.test=FALSE)) #  45.4 % explained deviance

# Check model fit
gam.check(m3bin) # k should be increased


# Increase k to 20
mB3bin20 <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB3bin20.rda"))

# Model summary
(mB3bin20_sum <- summary(mB3bin20, re.test=TRUE)) # 69.2% explained deviance --> THIS IS REPORTED IN PAPER (Table 5)

# Save model summary
save(mB3bin20_sum, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB3bin20_sum.rda", compress='xz')

print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB3bin20_sum.rda"))

# Print model statistics
mB3bin20_stats <- report_stats(mB3bin20)

# Save model statistics
save(mB3bin20_stats, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB3bin20_stats.rda", compress='xz')

# Check model fit
gam.check(m3bin20) # better! p-values are not very low anymore


```


## Add scores on cognitive tasks
```{r}
# Include scores on Stroop task, Dual task, and SART
mB4bin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(SartError_scale)
                  + s(Stroop_scale)
                  + s(DualScore_scale)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")


# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4bin.rda"))

# Model summary
(mB4bin_sum <- summary(mB4bin, re.test=TRUE)) #  % explained deviance; only Stroop significant

# Save model summary
save(mB4bin_sum, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4bin_sum.rda", compress='xz')

# Print statistics
mB4bin_stats <- report_stats(mB4bin)

# Save statistics
save(mB4bin_stats, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4bin_stats.rda", compress='xz')

print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4bin_stats.rda"))


# Remove score on SART
mB4abin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Stroop_scale)
                  + s(DualScore_scale)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4abin.rda"))

# Compare models
compareML(mB4bin, mB4abin, suggest.report = TRUE) # THIS IS REPORTED IN PAPER

# Remove score on Dual task
mB4bbin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Stroop_scale)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4bbin.rda"))

# Compare models
compareML(mB4abin, mB4bbin, suggest.report = TRUE) # THIS IS REPORTED IN PAPER

# Compare mB4bbin to mB3bin20 to test effect of Stroop
compareML(mB3bin20, mB4bbin, suggest.report = TRUE)


# Test the effect of Stroop for the interaction between Group and IdiomType
mB4cbin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Stroop_scale, by=GroupType)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4cbin.rda"))

# Model summary
(mB4cbin_sum <- summary(mB4cbin, re.test=TRUE))

# Save model summary
save(mB4cbin_sum, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4cbin_sum.rda")

# Test the effect of Stroop for the interaction between Group and Condition
mB4dbin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Stroop_scale, by=GroupCond)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4dbin.rda"))

# Model summary
(mB4dbin_sum <- summary(mB4dbin, re.test=TRUE))

# Save model summary
save(mB4dbin_sum, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4dbin_sum.rda")

# Test the effect of Stroop for the difference between conditions
mB4ebin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Stroop_scale, by=IsCompTwo)
                  + s(Stroop_scale, by=IsCompThree)
                  + s(Stroop_scale, by=IsOldCompTwo)
                  + s(Stroop_scale, by=IsOldCompThree)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4ebin.rda"))

# Model summary
(mB4ebin_sum <- summary(mB4ebin, re.test=FALSE))

# Report statistics
mB4ebin_stats <- report_stats(mB4ebin)

# Save statistics
save(mB4ebin_stats, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB4ebin_stats.rda", compress='xz')
```




## Test the effect of idiom literality
```{r}
# Fit model
mB5bin <- bam(Counts ~ GroupType
                  + s(Timebin, by=GroupType, k=20)
                  + s(Timebin, by=IsCompTwo, k=20)
                  + s(Timebin, by=IsCompThree, k=20)
                  + s(Timebin, by=IsOldCompTwo, k=20)
                  + s(Timebin, by=IsOldCompThree, k=20)
                  + s(Stroop_scale)
                  + s(Literality)
                  + s(Timebin, Participant, bs="fs", m=1)
                  + s(Timebin, Item, bs="fs", m=1)
                  + s(Event, bs="re"),
                  data=expBegin, discrete=TRUE, family="binomial")

# Load model after running in Peregrine
print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB5bin.rda"))

# Compare models
compareML(mB5bin, mB4bbin, suggest.report = TRUE) # THIS IS REPORTED IN THE PAPER

# Print statistics
mB5bin_stats <- report_stats(mB5bin)

# Save statistics
save(mB5bin_stats, file="G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/m5bin_stats.rda", compress='xz')

print(load("G:/Back-up Y-schijf 12.03.2020/Study 2 - Eye tracking + AD/Analysis/Models/mB5bin_stats.rda"))

```

